Improving the portuguese hyphenation rules

### 2023-05-02 article/article.tex
fix issue #5

Merely stating that an orthographic system is guided by phonological issues
does not necessarily mean that its hyphenation rules directly reflect the way a
word is pronounced. This is because the orthographic system operates according
to its own specific rules. For instance, although vowel clusters that produce a
single sound (i.e., digraphs) are pronounced within a single syllable in words
like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{bird},
their representation in writing determines how they are separated.
Specifically, different consonants within a digraph must remain together, while
different consonants are separated. As a result, we have \emph{i-lha} but \emph{car}.

>>>>

Merely stating that an orthographic system is guided by phonological issues
does not necessarily mean that its hyphenation rules directly reflect the way a
word is pronounced. This is because the orthographic system operates according
to its own specific rules. For instance, although vowel clusters that produce a
single sound (i.e., digraphs) are pronounced within a single syllable in words
like \emph{chave}, \emph{ilha}, \emph{shampoo}, \emph{carro}, and \emph{pássaro},
their representation in writing determines how they are separated.
Specifically, different consonants within a digraph must remain together, while
different consonants are separated. As a result, we have \emph{i-lha} but \emph{car}.
